### 2015-08-04 Irregular-occ/Irregular-occ.tex
.

%\texttt{ d  m year  h:m:s UT     ra\_\_\_dec\_\_\_J2000\_candidate     ra\_dec\_J2000\_target\_geocen     C/A    P/A     vel  Delta  R*   J*   H*   K*   long  loc. t.  off\_ra   off\_de pm ct f E\_ra E\_de pmra pmde} \tabularnewline
%\hline
% 05 01 2015  01 07  4.   09 32 20.9233 +15 35  10.584   09 32 20.9885 +15 35  12.220   1.888   29.94 -11.41  4.51 14.8 -0.6 -0.6 -0.6    22. 02:35     -31.0    -13.0 ok uc 0    0    0   -4    1 \tabularnewline
% 15 01 2015  01 03 15.   09 29  0.9265 +16 01  18.932   09 29  0.9610 +16 01  19.900   1.088   27.21 -13.17  4.45 14.8 -0.5 -0.5 -0.5    12. 01:52     -31.0    -13.0 ok uc 0    0    0   -2  -16 \tabularnewline
% 02 02 2015  08 03 30.   09 21 46.5321 +16 49  43.658   09 21 46.4857 +16 49  42.068   1.723  202.72 -14.32  4.40 16.0 -0.4 -0.4 -0.4   247. 00:32     -31.0    -13.0 ok uc 0    0    0    1   -8 \tabularnewline
% 14 02 2015  16 11 59.   09 16 41.4840 +17 18   2.448   09 16 41.4473 +17 18   0.976   1.563  199.68 -13.64  4.42 12.5 -0.4 -0.4 -0.4   112. 23:39     -31.0    -13.0 ok uc 0    0    0    5    0 \tabularnewline
% 25 02 2015  19 27 38.   09 12 25.6457 +17 38   6.563   09 12 25.6804 +17 38   8.217   1.727   16.72 -12.01  4.47 12.2 -0.6 -0.6 -0.6    51. 22:51     -31.0    -13.0 ok uc 0    0    0   -3    4 \tabularnewline
% 28 02 2015  09 17 38.   09 11 31.5455 +17 41  53.701   09 11 31.5720 +17 41  55.023   1.375   15.96 -11.50  4.49 14.1 -0.6 -0.6 -0.6   201. 22:40     -31.0    -13.0 ok uc 0    0    0  -16    6 \tabularnewline
% 03 03 2015  00 39 17.   09 10 38.6352 +17 45  26.467   09 10 38.6218 +17 45  25.758   0.734  195.15 -10.94  4.50 14.1 -0.7 -0.7 -0.7   327. 22:28     -31.0    -13.0 ok uc 0    0    0   -5    2 \tabularnewline
% 20 05 2015  08 59 41.   09 13 37.6521 +16 48  39.598   09 13 37.6915 +16 48  41.011   1.522   21.84  17.60  5.48 15.2 -0.1 -0.1 -0.1   126. 17:22     -31.0    -13.0 ok uc 0    0    0    0    0 \tabularnewline
% 22 05 2015  06 52 27.   09 14 25.8437 +16 44   5.646   09 14 25.8400 +16 44   5.511   0.147  201.62  18.32  5.51 16.4 -0.1 -0.1 -0.1   156. 17:16     -31.0    -13.0 ok uc 0    0    0  -13    2 \tabularnewline
% 02 06 2015  16 14 18.   09 19 46.8676 +16 14  30.501   09 19 46.8693 +16 14  30.569   0.078   20.53  22.38  5.67 14.5  0.1  0.1  0.1     6. 16:36     -31.0    -13.0 ok uc 0    0    0   -7  -15 \tabularnewline
% 06 06 2015  02 41  6.   09 21 34.2809 +16 04  53.249   09 21 34.2951 +16 04  53.800   0.588   20.32  23.54  5.71 16.4  0.2  0.2  0.2   206. 16:24     -31.0    -13.0 ok uc 0    0    0    2    5 \tabularnewline
% 08 06 2015  20 25 31.   09 23  3.2029 +15 57   1.059   09 23  3.2057 +15 57   1.170   0.122   20.13  24.44  5.75 16.7  0.2  0.2  0.2   297. 16:15     -31.0    -13.0 ok uc 0    0    0   -3   -6 \tabularnewline
% 09 06 2015  22 29 56.   09 23 39.2777 +15 53  51.969   09 23 39.2451 +15 53  50.681   1.372  200.09  24.80  5.76 11.6  0.2  0.2  0.2   265. 16:11     -31.0    -13.0 ok uc 0    0    0    5  -24 \tabularnewline
% 20 06 2015  16 15 15.   09 29 57.6850 +15 21   0.007   09 29 57.7127 +15 21   1.135   1.198   19.56  28.11  5.90 16.4  0.4  0.4  0.4   350. 15:35     -31.0    -13.0 ok uc 0    0    0   -8   -1 \tabularnewline
% 05 07 2015  17 02 21.   09 39 45.6144 +14 31  18.362   09 39 45.6473 +14 31  19.747   1.465   19.04  32.07  6.06 16.7  0.5  0.5  0.5   326. 14:46     -31.0    -13.0 ok uc 0    0    0    0   -9 \tabularnewline
% 16 07 2015  03 15 38.   09 47  5.8941 +13 54  48.764   09 47  5.8853 +13 54  48.387   0.400  198.77  34.42  6.15 16.4  0.6  0.6  0.6   164. 14:12     -31.0    -13.0 ok uc 0    0    0  -19  -10 \tabularnewline
% 07 10 2015  21 52 34.   10 53 40.1835 +08 21   0.489   10 53 40.1726 +08 21   0.054   0.465  200.31  39.31  6.25 16.6  0.7  0.7  0.7   179. 09:48     -31.0    -13.0 ok uc 0    0    0  -13   -7 \tabularnewline
% 23 10 2015  07 54 50.   11 05 26.6037 +07 14  32.030   11 05 26.5789 +07 14  31.083   1.017  201.33  36.11  6.12 15.5  0.6  0.6  0.6    16. 08:59     -31.0    -13.0 ok uc 0    0    0   -7   -4 \tabularnewline
% 31 10 2015  00 24 19.   11 10 56.2964 +06 42   7.110   11 10 56.3414 +06 42   8.782   1.801   21.84  33.94  6.04 16.9  0.6  0.6  0.6   123. 08:34     -31.0    -13.0 ok uc 0    0    0   -4  -13 \tabularnewline
% 07 11 2015  21 22 53.   11 16 14.3041 +06 10   5.194   11 16 14.2963 +06 10   4.912   0.306  202.36  31.33  5.94 16.2  0.5  0.5  0.5   162. 08:09     -31.0    -13.0 ok uc 0    0    0    0    0 \tabularnewline
% 08 11 2015  04 27 21.   11 16 25.7881 +06 08  55.566   11 16 25.7606 +06 08  54.571   1.077  202.38  31.23  5.94 16.9  0.5  0.5  0.5    55. 08:08     -31.0    -13.0 ok uc 0    0    0    9  -10 \tabularnewline

@@

% 31 10 2015  00 24 19.   11 10 56.2964 +06 42   7.110   11 10 56.3414 +06 42   8.782   1.801   21.84  33.94  6.04 16.9  0.6  0.6  0.6   123. 08:34     -31.0    -13.0 ok uc 0    0    0   -4  -13 \tabularnewline
% 07 11 2015  21 22 53.   11 16 14.3041 +06 10   5.194   11 16 14.2963 +06 10   4.912   0.306  202.36  31.33  5.94 16.2  0.5  0.5  0.5   162. 08:09     -31.0    -13.0 ok uc 0    0    0    0    0 \tabularnewline
% 08 11 2015  04 27 21.   11 16 25.7881 +06 08  55.566   11 16 25.7606 +06 08  54.571   1.077  202.38  31.23  5.94 16.9  0.5  0.5  0.5    55. 08:08     -31.0    -13.0 ok uc 0    0    0    9  -10 \tabularnewline
% 09 11 2015  09 01  4.   11 17 11.6890 +06 04  11.474   11 17 11.7030 +06 04  11.980   0.549   22.45  30.79  5.92 15.9  0.5  0.5  0.5   346. 08:04     -31.0    -13.0 ok uc 0    0    0   19  -13 \tabularnewline
% 11 11 2015  12 58 46.   11 18 33.8286 +05 55  43.695   11 18 33.8357 +05 55  43.946   0.274   22.59  29.98  5.90 14.6  0.4  0.4  0.4   285. 07:57     -31.0    -13.0 ok uc 0    0    0  -14    1 \tabularnewline
% 12 11 2015  20 14 22.   11 19 22.2740 +05 50  40.732   11 19 22.3183 +05 50  42.312   1.713   22.68  29.48  5.88 15.7  0.4  0.4  0.4   175. 07:52     -31.0    -13.0 ok uc 0    0    0   -7   -4 \tabularnewline
% 04 12 2015  03 31 56.   11 30 41.9967 +04 37  36.039   11 30 42.0020 +04 37  36.217   0.196   24.18  20.14  5.56 15.0  0.0  0.0  0.0    47. 06:40     -31.0    -13.0 ok uc 0    0    0    5   -9 \tabularnewline
\hline
\end{tabular}
\par\end{centering}
\textbf{Notes}. Occultation table: day of the year and UTC time of the prediction; right ascension and declination of the occulted star - in the original table, these coordinates are immediately followed by the geocentric astrometric equatorial coordinates (corrected for the offset or ephemeris method), not presented here, of the occulting body; C/A: the geocentric closest approach, in arcseconds; P/A: the planet position angle with respect to the occulted star at C/A, in degrees; velocity in plane of sky, in km s$^{-1}$: positive = prograde, negative = retrograde; D: planet range to Earth, in AU; R*, J*, H*, K*: normalized magnitudes to a common shadow velocity of 20 km s$^{-1}$ by the relationship $\textrm{Mag}* = \textrm{Mag}_{\textrm{actual}} + 2.5 \times \log 10 \left(\frac{\textrm{velocity}} {20 \textrm{km}\, \textrm{s}^{-1}} \right)$. A value of 50.0 means that the star is not in the 2MASS; $\lambda$: east longitude of subplanet point in degrees, positive towards east; LST: UT + $\lambda$: local solar time at subplanet point, hh:mm; $\Delta e_{\alpha *}$ and $\Delta e_{\delta}$:offset in mas applied to the ephemeris right ascension and declination, respectively; pm: ok = proper motion applied, no = no proper motion applied; catalogue cross-identification (ct) = uc (UCAC2), 2m (2MASS), fs (field star); f = multiplicity flag (see Table 3); $E_{\alpha *}$ and $E_{\delta}$: uncertainties (mas) in right ascension and declination. A value of 9999 means that there was no estimation of the respective uncertainty; $\mu_{\alpha *}$ and $\mu_{\delta}$: proper motions in right ascension and declination, respectively (mas/year).
\label{Tab: occ-list}
\end{table*}

@@

This test consists in observing the object and star to be occulted near the event when the two objects are present in the same field of view, preferably when the objects are close to each other. Thus the relative positions between the two objects will have minimal influence of the errors of the catalogue of stars used and possible field distortions.

@@

\begin{figure*}
\begin{centering}
\subfigure[Nominal prediction]{\includegraphics[scale=0.19]{figures/Himalia1_2015-03-03T00:39:25.png}  \label{Fig: occ-Himalia-nooff}}
\subfigure[\textcolor{red}{Offset de Himalia a partir do ajuste}]{\includegraphics[scale=0.19]{figures/Himalia2_2015-03-03T00:39:18.png}  \label{Fig: occ-Himalia-ajuste}}
\subfigure[February 22 observations (different FOVs)]{\includegraphics[scale=0.19]{figures/Himalia3_2015-03-03T00:39:40.png}   \label{Fig: occ-Himalia-off22fev}}
\subfigure[March 03 observation (same FOV)]{\includegraphics[scale=0.19]{figures/Himalia4_2015-03-03T00:39:15.png}   \label{Fig: occ-Himalia-off03mar}}
\caption{Predictions for Himalia: The big red dot show the geocentric closest approach of the shadow. The small red ones are the center of the shadow separated by one minute. The straight lines show the size of the shadow. \ref{Fig: occ-Himalia-nooff} is the map using the nominal positions of the star and satellite. \ref{Fig: occ-Himalia-ajuste} shows the shadow given an estimated offset for the position of Himalia related to the JPL ephemeris obtained in section \ref{Sec: Offset}. In \ref{Fig: occ-Himalia-off22fev} we apply offsets to the positions of star and satellite accordingly the observations made at February 22. In \ref{Fig: occ-Himalia-off03mar} is as in \ref{Fig: occ-Himalia-off22fev} but with observations made at March 03 when the objects were close to each other. \textcolor{red}{Figuras ainda serão mudadas. Colocadas para visualização}}
\label{Fig: occ-Himalia}
\end{centering}
\end{figure*}

>>>>

 31 10 2015 & 00 24 19. &  11 10 56.2964 & +06 42  07.110 &  1.801 &  21.84 & 33.94 &  6.04 & 16.9 &  123. & 08:34 & -31.0 & -13.0 & ok & uc & 0  &  0 & -4 & -13 \tabularnewline
 07 11 2015 &  21 22 53. &  11 16 14.3041 & +06 10  05.194 &  0.306 &  202.36 & 31.33 & 5.94 & 16.2 & 162. & 08:09 & -31.0 & -13.0 & ok & uc & 0 & 0 & 0 & 0 \tabularnewline
 08 11 2015 & 04 27 21. &  11 16 25.7881 & +06 08  55.566 & 1.077 & 202.38 & 31.23 & 5.94 & 16.9 & 55. & 08:08 & -31.0 & -13.0 & ok & uc & 0 & 0 & 9 & -10 \tabularnewline

@@

\end{tabular}
\par\end{centering}
\textbf{Notes}. Occultation table: day of the year and UTC time of the prediction; right ascension and declination of the occulted star - in the original table, these coordinates are immediately followed by the geocentric astrometric equatorial coordinates (corrected for the offset or ephemeris method), not presented here, of the occulting body; C/A: the geocentric closest approach, in arcseconds; P/A: the planet position angle with respect to the occulted star at C/A, in degrees; velocity in plane of sky, in km s$^{-1}$: positive = prograde, negative = retrograde; D: planet range to Earth, in AU; R*: normalized magnitude to a common shadow velocity of 20 km s$^{-1}$ by the relationship $\textrm{Mag}* = \textrm{Mag}_{\textrm{actual}} + 2.5 \times \log 10 \left(\frac{\textrm{velocity}} {20 \textrm{km}\, \textrm{s}^{-1}} \right)$. A value of 50.0 means that the star is not in the 2MASS; $\lambda$: east longitude of subplanet point in degrees, positive towards east; LST: UT + $\lambda$: local solar time at subplanet point, hh:mm; $\Delta e_{\alpha *}$ and $\Delta e_{\delta}$:offset in mas applied to the ephemeris right ascension and declination, respectively; pm: ok = proper motion applied, no = no proper motion applied; catalogue cross-identification (ct) = uc (UCAC2), 2m (2MASS), fs (field star); f = multiplicity flag (see Table 3); $E_{\alpha *}$ and $E_{\delta}$: uncertainties (mas) in right ascension and declination. A value of 9999 means that there was no estimation of the respective uncertainty; $\mu_{\alpha *}$ and $\mu_{\delta}$: proper motions in right ascension and declination, respectively (mas/year).
\label{Tab: occ-list}
\end{table*}

@@

This test consists in observing the object and star to be occulted near the event when the two objects are present in the same field of view, preferably when the objects are close to each other. Thus the relative positions between the two objects will have minimal influence of the errors of the catalogue of stars used and possible field distortions \citep[and references therein]{Peng2008}. The offsets of the positions of the star and the satellites will be used to correct the predictions.

@@

\begin{figure*}
\begin{centering}
\subfigure[Nominal prediction]{\includegraphics[scale=0.19]{figures/Himalia1_2015-03-03T00:39:25.png}  \label{Fig: occ-Himalia-nooff}}
\subfigure[\textcolor{red}{Offset de Himalia a partir do ajuste}]{\includegraphics[scale=0.19]{figures/Himalia2_2015-03-03T00:39:18.png}  \label{Fig: occ-Himalia-ajuste}}
\subfigure[Observation at February 22 (different FOVs)]{\includegraphics[scale=0.19]{figures/Himalia3_2015-03-03T00:39:40.png}   \label{Fig: occ-Himalia-off22fev}}
\subfigure[Observation at March 03 (same FOV)]{\includegraphics[scale=0.19]{figures/Himalia4_2015-03-03T00:39:15.png}   \label{Fig: occ-Himalia-off03mar}}
\caption{Predictions for Himalia: The big red dot show the geocentric closest approach of the shadow. The small red ones are the center of the shadow separated by one minute. The straight lines show the size of the shadow. \ref{Fig: occ-Himalia-nooff} is the map using the nominal positions of the star and satellite. \ref{Fig: occ-Himalia-ajuste} shows the shadow given an estimated offset for the position of Himalia related to the JPL ephemeris obtained in section \ref{Sec: Offset}. In \ref{Fig: occ-Himalia-off22fev} we apply offsets to the positions of star and satellite accordingly the observations made at February 22. In \ref{Fig: occ-Himalia-off03mar} is as in \ref{Fig: occ-Himalia-off22fev} but with observations made at March 03 when the objects were close to each other. \textcolor{red}{Figuras ainda serão mudadas. Colocadas para visualização}}
\label{Fig: occ-Himalia}
\end{centering}
\end{figure*}
